### 2024-09-04 download-football-data.qmd
20240904 - data update before start of 2024 season

```{r}
library("ffanalytics")
library("petersenlab")
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

nfl_advancedStatsPFR_pass_seasonal_raw <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("pass"),
    summary_level = c("season")))

nfl_advancedStatsPFR_pass_weekly_raw <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("pass"),
    summary_level = c("week")))

@@

@@

players_projections_seasonal_raw <- ffanalytics::scrape_data(
  season = NULL, # NULL grabs the current season
  week = 0) # NULL grabs seasonal projections; NULL grabs the current week
```

@@

save(
  players_projections_seasonal_raw,
  file = "./data/players_projections_seasonal_raw.RData"
)
```

@@

```{r}
load(file = "./data/players_projections_seasonal_raw.RData")
```

The `players_projections_seasonal_raw` object is in `player`-`position`-`projection source` form.
That is, each row should be uniquely identified by the combination of `id`, `pos`  and `data_src`.
Each row should also be uniquely identified by the combination of `player`, `pos`, and `data_src`.

@@

players_projections_seasonal_raw %>% 
  bind_rows() %>% 
  select(player, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()
```

@@

Now, modify the scoring settings to match our league settings:

@@

scoring_obj$pass$pass_int <- -2
scoring_obj$misc$fumbles_lost <- -2
scoring_obj$idp$idp_fum_force <- -2
```

@@

```{r}
players_projectedPoints_seasonal <- ffanalytics:::impute_and_score_sources(
  data_result = players_projections_seasonal_raw,
  scoring_rules = scoring_obj)
```

@@

```{r}
players_projectedStatsAverage_seasonal <- ffanalytics::projections_table(
  players_projections_seasonal_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = TRUE)

players_projectedPointsAverage_seasonal <- ffanalytics::projections_table(
  players_projections_seasonal_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = FALSE)
```

The `players_projectedPoints_seasonal`, `players_projectedStatsAverage_seasonal`, and `players_projectedPointsAverage_seasonal` objects are in `player`-`average type`-`position` form.
That is, each row should be uniquely identified by the combination of `id`, `avg_type`  and `pos` (or `position`).

@@

players_projectedPointsAverage_seasonal %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()
```

@@

```{r}
players_projections_seasonal_average <- full_join(
  players_projectedPointsAverage_seasonal,
  players_projectedStatsAverage_seasonal,
  by = c("id","avg_type","pos" = "position")
)
```

@@

```{r}
players_projections_seasonal_average %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()
```

@@

players_projections_seasonal_average <- players_projections_seasonal_average %>% 
  add_ecr() %>% 
  add_adp() %>% 
  add_aav() %>%
  add_uncertainty() %>% 
  add_player_info()
```

@@

save(
  players_projectedPoints_seasonal,
  file = "./data/players_projectedPoints_seasonal.RData"
)

save(
  players_projections_seasonal_average,
  file = "./data/players_projections_seasonal_average.RData"
)
```

@@

```{r}
load(file = "./data/players_projectedPoints_seasonal.RData")
load(file = "./data/players_projections_seasonal_average.RData")
```

@@

# Merge with player info
player_age_offense <- dplyr::left_join(
  player_game_birthdate_gameday_offense,
  nfl_players %>% select(-birth_date, -season, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id"))

player_age_defense <- dplyr::left_join(
  player_game_birthdate_gameday_defense,
  nfl_players %>% select(-birth_date, -season, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id"))

player_age_kicking <- dplyr::left_join(
  player_game_birthdate_gameday_kicking,
  nfl_players %>% select(-birth_date, -season, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id"))

@@

```{r}
# Merge player info with seasonal stats
player_stats_seasonal_offense <- dplyr::full_join(
  nfl_actualStats_offense_seasonal,
  nfl_players %>% select(-position, -position_group, -season, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id")
)

player_stats_seasonal_defense <- dplyr::full_join(
  nfl_actualStats_defense_seasonal,
  nfl_players %>% select(-position, -position_group, -season, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id")
)

player_stats_seasonal_kicking <- dplyr::full_join(
  nfl_actualStats_kicking_seasonal,
  nfl_players %>% select(-position, -position_group, -season, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id")
)

>>>>

```{r}
library("ffanalytics") # to install: install.packages("remotes"); remotes::install_github("FantasyFootballAnalytics/ffanalytics")
library("petersenlab") # to install: install.packages("remotes"); remotes::install_github("DevPsyLab/petersenlab")
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

# Seasonal Data
nfl_advancedStatsPFR_pass_seasonal_raw <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("pass"),
    summary_level = c("season")))

@@

# Weekly Data
nfl_advancedStatsPFR_pass_weekly_raw <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("pass"),
    summary_level = c("week")))

@@

# Seasonal Projections
players_projections_seasonal_raw <- ffanalytics::scrape_data(
  season = NULL, # NULL grabs the current season
  week = 0) # NULL grabs seasonal projections; NULL grabs the current week

# Weekly Projections
players_projections_weekly_raw <- ffanalytics::scrape_data(
  season = NULL, # NULL grabs the current season
  week = NULL) # NULL grabs the current week
```

@@

save(
  players_projections_seasonal_raw,
  file = "./data/players_projections_seasonal_raw.RData"
)

save(
  players_projections_weekly_raw,
  file = "./data/players_projections_weekly_raw.RData"
)
```

@@

```{r}
load(file = "./data/players_projections_seasonal_raw.RData")
load(file = "./data/players_projections_weekly_raw.RData")
```

The `players_projections_seasonal_raw` and `players_projections_weekly_raw` object is in `player`-`position`-`projection source` form.
That is, each row should be uniquely identified by the combination of `id`, `pos`  and `data_src`.
Each row should also be uniquely identified by the combination of `player`, `pos`, and `data_src`.

@@

players_projections_seasonal_raw %>% 
  bind_rows() %>% 
  select(player, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()

players_projections_weekly_raw %>% 
  bind_rows() %>% 
  select(id, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()

players_projections_weekly_raw %>% 
  bind_rows() %>% 
  select(player, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()
```

@@

Now, modify the scoring settings to match our league settings (based on [scoring settings](https://support.nfl.com/hc/en-us/articles/4989179237404-Scoring) for fantasy leagues on NFL.com):

@@

# Offense
scoring_obj$pass$pass_int <- -2
scoring_obj$rec$rec <- 1
scoring_obj$misc$fumbles_lost <- -2

# Kickers
scoring_obj$kick$fg_4049 <- 3

# Defense/Special Teams
scoring_obj$pts_bracket[[3]]$threshold <- 13
scoring_obj$pts_bracket[[3]]$points <- 4

scoring_obj$pts_bracket[[4]]$threshold <- 20
scoring_obj$pts_bracket[[4]]$points <- 1

scoring_obj$pts_bracket[[5]]$threshold <- 27
scoring_obj$pts_bracket[[5]]$points <- 0

scoring_obj$pts_bracket[[6]] <- list(
  threshold = 34,
  points = -1
)

scoring_obj$pts_bracket[[7]] <- list(
  threshold = 99,
  points = -4
)
```

# My Yahoo League
scoring_obj <- scoring_obj_default

scoring_obj$pass$pass_int <- -3
scoring_obj$misc$fumbles_lost <- -3
scoring_obj$idp$idp_fum_force <- -2
```

@@

```{r}
players_projectedPoints_seasonal <- ffanalytics:::impute_and_score_sources(
  data_result = players_projections_seasonal_raw,
  scoring_rules = scoring_obj)

players_projectedPoints_weekly <- ffanalytics:::impute_and_score_sources(
  data_result = players_projections_weekly_raw,
  scoring_rules = scoring_obj)
```

@@

```{r}
# Seasonal Projections
players_projectedStatsAverage_seasonal <- ffanalytics::projections_table(
  players_projections_seasonal_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = TRUE)

players_projectedPointsAverage_seasonal <- ffanalytics::projections_table(
  players_projections_seasonal_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = FALSE)

# Weekly Projections
players_projectedStatsAverage_weekly <- ffanalytics::projections_table(
  players_projections_weekly_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = TRUE)

players_projectedPointsAverage_weekly <- ffanalytics::projections_table(
  players_projections_weekly_raw,
  scoring_rules = scoring_obj,
  return_raw_stats = FALSE)
```

The `players_projectedPoints_seasonal`, `players_projectedStatsAverage_seasonal`, `players_projectedPointsAverage_seasonal`, `players_projectedPoints_weekly`, `players_projectedStatsAverage_weekly`, and `players_projectedPointsAverage_weekly` objects are in `player`-`average type`-`position` form.
That is, each row should be uniquely identified by the combination of `id`, `avg_type`  and `pos` (or `position`).

@@

players_projectedPointsAverage_seasonal %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()

players_projectedPoints_weekly %>% 
  bind_rows() %>% 
  select(id, pos, data_src, everything()) %>%
  arrange(player, id, pos, data_src) %>% 
  group_by(id, pos, data_src) %>% 
  filter(n() > 1, !is.na(id)) %>% 
  head()

players_projectedStatsAverage_weekly %>% 
  group_by(id, avg_type, position) %>% 
  filter(n() > 1) %>% 
  head()

players_projectedPointsAverage_weekly %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()
```

@@

```{r}
players_projections_seasonal_average <- full_join(
  players_projectedPointsAverage_seasonal,
  players_projectedStatsAverage_seasonal,
  by = c("id","avg_type","pos" = "position")
)

players_projections_weekly_average <- full_join(
  players_projectedPointsAverage_weekly,
  players_projectedStatsAverage_weekly,
  by = c("id","avg_type","pos" = "position")
)
```

@@

```{r}
players_projections_seasonal_average %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()

players_projections_weekly_average %>% 
  group_by(id, avg_type, pos) %>% 
  filter(n() > 1) %>% 
  head()
```

@@

players_projections_seasonal_average <- players_projections_seasonal_average %>% 
  add_ecr() %>% 
  add_adp() %>% 
  add_aav() %>%
  add_uncertainty() %>% 
  add_player_info()

players_projections_weekly_average <- players_projections_weekly_average %>% 
  add_ecr() %>% 
  #add_uncertainty() %>% # currently throws an error
  add_player_info()
```

@@

save(
  players_projectedPoints_seasonal, players_projections_seasonal_average,
  file = "./data/players_projectedPoints_seasonal.RData"
)

save(
  players_projectedPoints_weekly, players_projections_weekly_average,
  file = "./data/players_projectedPoints_weekly.RData"
)
```

@@

```{r}
load(file = "./data/players_projectedPoints_seasonal.RData")
load(file = "./data/players_projectedPoints_weekly.RData")
```

@@

# Merge with player info
player_age_offense <- dplyr::left_join(
  player_game_birthdate_gameday_offense,
  nfl_players %>% select(-birth_date, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id"))

player_age_defense <- dplyr::left_join(
  player_game_birthdate_gameday_defense,
  nfl_players %>% select(-birth_date, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id"))

player_age_kicking <- dplyr::left_join(
  player_game_birthdate_gameday_kicking,
  nfl_players %>% select(-birth_date, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id"))

@@

```{r}
# Merge player info with seasonal stats
player_stats_seasonal_offense <- dplyr::full_join(
  nfl_actualStats_offense_seasonal,
  nfl_players %>% select(-position, -position_group, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id")
)

player_stats_seasonal_defense <- dplyr::full_join(
  nfl_actualStats_defense_seasonal,
  nfl_players %>% select(-position, -position_group, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id")
)

player_stats_seasonal_kicking <- dplyr::full_join(
  nfl_actualStats_kicking_seasonal,
  nfl_players %>% select(-position, -position_group, -team_abbr, - team_seq),
  by = c("player_id" = "gsis_id")
)
